Approximation as Differentiation

### 2025-06-09 main/first-order.tex
LatGal as a CMon-category.

$\LatGal$ is enriched in $\CMon$ (in fact in $\SemiLat$, the category of semilattices, but again $\CMon$ will
do for our purposes). The meet-preserving maps from $X$ to $Y$ can be added pointwise using $\meet$, since $(f
\meet g)(x) = f(x) \meet g(x)$ preserves meets, with the constant map $\top = x \mapsto \top_Y$ as a zero;
dually the join-preserving maps from $Y$ to $X$ can be added pointwise using $\join$, with the constant map
$\bot = y \mapsto \bot_X$ as a zero. Since these constructions come in adjoint pairs, the hom-set
$\LatGal(X,Y)$ forms a commutative monoid with $0$ given by the Galois connection $\bot \adj \top$ and
addition $(f \adj g) + (f' \adj g') = (f \join f') \adj (g \meet g')$.

>>>>

$\LatGal$ is enriched in $\CMon$ (in fact in $\SemiLat$, the category of semilattices, but again $\CMon$ will
do for our purposes). The meet-preserving maps from $X$ to $Y$ can be added pointwise using $\meet$, since $(f
\meet g)(x) = f(x) \meet g(x)$ preserves meets, with the constant map $\top = x \mapsto \top_Y$ as a zero;
dually the join-preserving maps from $Y$ to $X$ can be added pointwise using $\join$, with the constant map
$\bot = y \mapsto \bot_X$ as a zero. Since these constructions come in adjoint pairs, the hom-set
$\LatGal(X,Y)$ forms a commutative monoid with $0$ given by the Galois connection $\bot \adj \top$ and
addition $(f \adj g) + (f' \adj g') = (f \join f') \adj (g \meet g')$, with composition bilinear.
